Supplementary Materials from: \textit{Innovation and elaboration on the avian tree of life}; Science Advances, in review

### 2023-06-08 Manuscript/supplementaries.tex
Update supplementaries.tex

\begin{figure}[H]
\centering
   \includegraphics[width=0.9\textwidth]{Figures/correlations_fable.pdf}
\caption{Posterior distributions of the correlation between $elaboration_{species}$ and $innovation_{species}$ for each super-orders in Fig. \ref{Fig:figure_correlations}. Species' projection onto the clade-wide phylogenetic major axis of beak variation corresponds to the correlation scores in Fig. \ref{Fig:figure_correlations}A-B and species' projections onto their own super-order's phylogenetic major axis of beak variation corresponds to the correlation scores in Fig. \ref{Fig:figure_correlations}C.}
\label{Fig:fable_correlations_supplementary}
\end{figure}

>>>>

\begin{figure}[H]
\centering
   \includegraphics[width=0.9\textwidth]{Figures/correlations_fable_super_orders.pdf}
\caption{Posterior distributions of the correlation between $elaboration_{species}$ and $innovation_{species}$ for each super-orders in Fig. \ref{Fig:figure_correlations}.
A) Species' projection onto the class-wide phylogenetic major axes of beak variation (corresponding to the correlation scores in Fig. \ref{Fig:figure_correlations}A-B); B) Species' projection onto the super-orders' phylogenetic major axes of beak variation (corresponding to the correlation scores in Fig. \ref{Fig:figure_correlations}C).}
\label{Fig:fable_correlations_supplementary}
\end{figure}
